Strategies for thorium fuel cycle transition in the SD-TMSR

### 2020-02-11 paper/highlights/highlights.tex
Highlights and minor changes

\begin{document}
\begin{frontmatter}
\title{Strategies for thorium fuel cycle transition in the SD-TMSR}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
       \item  
       \item  
       \item 
       \item  
       \item  
\end{itemize}
\end{document}

>>>>

\begin{document}
\begin{frontmatter}
\title{Strategies for thorium fuel cycle transition in the SD-TMSR}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
	\item Five initial fissile loadings have been studied for transitioning to the thorium fuel cycle in the SD-TMSR.
	\item The MSR burnup routine provided by SERPENT-2 is used to simulate the online reprocessing and refueling in the SD-TMSR.
	\item The dynamics of $k_{eff}$, major isotopes mass, and essential safety parameters have been investigated.
	\item The neutron energy spectrum shift during the reactor operation was calculated.
	\item Temperature coefficient of reactivity evolution during SD-TMSR operation are investigated.
\end{itemize}
\end{document}
